Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-04-29 thesis/paper/thesis.tex
law 3

\subsection{3 Self Regulation — E-type system evolution processes are self-regulating with the distribution of product and process measures close to normal}
If we look at the system growth as a normal distribution curve, it grew slowly in the beginning (1.0-1.4) and right now (2.0) we're in the peak of the curve and she said about hte future that it was going to be slow with few changes.

Post 2.0 - The API will continue to improve, but in they are far away in the future. If there is a new API coming, there will not be a big bang this time but instead incremental steps. For example adding new suitable features for partners. It won’t be a 2.0->3.0 big bang again.

>>>>

\subsection{3 Self Regulation — E-type system evolution processes are self-regulating with the distribution of product and process measures close to normal}
When version 1.4 was introduced, no new functionality or re-structuring was introduced. Version 1.4 only added support for additional build platforms. When comparing the changes introduced in 2.0 to the ones previously introduced, it is clear that the growth of the API has increased gradually. During the interview it was also mentioned that the future plans for the API did not include any major changes, and that only a few minor changes were planned in the near future. The future updates to the API will also be made incrementally, and there will not be a big bang update similar to the one of 2.0. This supports that Law \#3 can be applied to APIs, assuming that the current stage of the life-cycle of the API can be considered as the center of the normal distribution curve of the APIs growth.
